Manuscript

### 2022-04-20 analysis/manuscript.Rmd
wflow_publish("analysis/manuscript.Rmd")
adding manuscript tables

interesting_phenotypes <- c("Basal metabolic rate", "Place of birth in UK - north co-ordinate", 
                            "Systolic blood pressure, automated reading", "Standing height", 
                            "Weight", "Forced vital capacity (FVC), Best measure",
                            "Basophill count", "Pulse rate, automated reading")

@@

corr_vs_MR_effects_plot <- ggplot2::ggplot(data = corr_vs_MR_effects_dat, ggplot2::aes(x = Correlation,
                                                       y = MR_est, 
                                                       label = Phenotype, 
                                                       color = factor(diff_p_sig)),) +
  geom_point(alpha = 1.2) +
  scale_color_manual(values = custom_col[c(1,2)], labels=c("Non-significant","BF-signifncant difference")) +
  #geom_text(show.legend = FALSE) +
  geom_abline(slope=1, intercept=0) +

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = MR_est - IVW_se, ymax = MR_est + IVW_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = Correlation - couple_r_se, xmax = Correlation + couple_r_se),
    colour = "grey",
    width = 0
  ) +

  theme_minimal() +
  theme(legend.text=element_text(size=11)) +
  #geom_text(aes(x=1,y=2,label=""),show.legend=F) +
  ggplot2::labs(x = paste0("Couple correlation"),
                y = paste("Standardized MR effect")) +
  theme(legend.position="bottom") + theme(legend.title=element_blank()) +
  geom_text_repel(data = subset(corr_vs_MR_effects_dat, label_phenos==TRUE),
                  nudge_y = -0.25 - subset(corr_vs_MR_effects_dat, label_phenos==TRUE)$MR_est, size = 3.25,
                  direction = "x", show.legend = FALSE )

@@

number_of_potential_confounders <- dim(corr_potential_trait_confounders_pos)[1]/dim(corr_vs_MR_effects_sig_dat)[1]

@@

sig_confounders <- corr_potential_trait_confounders_pos %>% filter(sig_confounder) %>% group_by(outcome_ID) %>%
  arrange(-corr_due_to_confounding_ratio) %>%
  mutate(total_potential_confounders = n()) %>%
  dplyr::summarize(description = outcome_description[1],
                   total_potential_confounders = total_potential_confounders[1],
                   potential_confounders = paste0(exposure_description, collapse = "; "), 
                   max_C = max(corr_due_to_confounding), 
                   min_C = min(corr_due_to_confounding)) %>%
  dplyr::rename(trait_ID = outcome_ID) %>%
  dplyr::rename(trait_description = description) %>% 
  dplyr::select(trait_description, trait_ID, everything())

sig_confounders_top5 <- corr_potential_trait_confounders_pos %>% filter(sig_confounder) %>% group_by(outcome_ID) %>%
  arrange(-corr_due_to_confounding_ratio) %>%
  mutate(total_potential_confounders = n()) %>%
  slice_head(n = 5) %>%
  #mutate(potential_confounders = paste0(exposure_description, collapse = "; ")) %>%
  dplyr::summarize(trait_description = outcome_description[1],
                   total_potential_confounders = total_potential_confounders[1],
                   top5_potential_confounders = paste0(exposure_description, collapse = "; "), 
                   max_C = max(corr_due_to_confounding), 
                   min_C = min(corr_due_to_confounding)) %>%
  dplyr::rename(trait_ID = outcome_ID) %>%
  left_join(corr_vs_MR_effects_sig_dat.DT, by = c("trait_description", "trait_ID")) %>%
  dplyr::select(trait_description, trait_ID, couple_r, IVW_beta, IVW_pval,everything())

@@

```{r max_C_plot, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), message=FALSE}

@@

  dplyr::rename(Z_beta = IVW_beta) %>%
  dplyr::rename(Z_se = IVW_se) %>%
  dplyr::rename(Z_pval = IVW_pval) %>%
  mutate(Z_sq_beta = Z_beta^2) %>%
  mutate(Z_sq_se = sqrt(4*Z_beta^2*Z_se^2+2*Z_se^4)) %>%
  dplyr::rename(Z_AM_beta = exposure_ID_AM_IVW_beta) %>%
  dplyr::rename(Z_AM_se = exposure_ID_AM_IVW_se) %>%
  mutate(Z_prod = Z_sq_beta*Z_AM_beta) %>%
  mutate(Z_prod_var = variance_of_product(Z_sq_beta, Z_sq_se, Z_AM_beta, Z_AM_se)) %>%
  mutate(Z_prod_se = sqrt(Z_prod_var)) %>%
  mutate(same_trait_corr_minus_MR_est_se = sqrt(variance_of_sum(outcome_ID_IVW_se, outcome_ID_couple_r_se)))

max_C_plot <- ggplot2::ggplot(data = max_C_data, ggplot2::aes(x = corr_due_to_confounding,
                                                       y = same_trait_corr_minus_MR_est)) +
  geom_point(alpha = 1.2) +
  #scale_color_manual(values = custom_col[c(1,2)], labels=c("Non-significant","BF-signifncant difference")) +
  #geom_text(show.legend = FALSE) +
  geom_abline(slope=1, intercept=0) +

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = same_trait_corr_minus_MR_est - same_trait_corr_minus_MR_est_se, ymax = same_trait_corr_minus_MR_est + same_trait_corr_minus_MR_est_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = corr_due_to_confounding - Z_prod_se, xmax = corr_due_to_confounding + Z_prod_se),
    colour = "grey",
    width = 0
  ) +

  theme_minimal() +
  ggplot2::labs(x = paste0("max C"),
                y = paste("Correlation - MR-estimate")) +
  theme(legend.title=element_blank()) +
  #geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  theme_ipsum()

@@

@@

nominally_sig_sex_differences <- AM_result_sig_nom.DT %>% pivot_wider(names_from = exposure_sex, values_from = c(IVW_beta, IVW_se, IVW_pval)) 
# write.table(nominally_sig_sex_differences, "docs/manuscript_tables/nominally_sig_sex_differences.txt", row.names = F, sep=",", quote = F)

@@

pheno_corr_pearson_sig <- binned_pheno_corr_summary %>% filter(bin_slope_pval_pearson < 0.05/num_tests_by_PCs) %>% arrange(group)

@@

```{r, pheno_binned_figs, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), echo = FALSE, out.width = "200%", dpi=600}

@@

@@

# write.table(corr_impact_ratios_summary, "docs/manuscript_tables/corr_impact_ratios_summary.txt", row.names = F, sep=",", quote = F)
```

@@

@@

corr_impact_by_traits_causal_summary %>%
  kbl() %>%
  kable_styling()

@@

*A note on the number of traits:*

We tested the impact of `trait_interest` on couple correlation amongst all traits in our couple MR framework (number of traits = `r dim(household_MR_summary_AM)[1]`) with the exception of birth place coordinates (2 each [N and E]), we also removed the trait itself from the confounder analysis where applicable (in the case of traits `20016_irnt`, `738` and `845`). [Trait `189_irnt` was not included in our final couple MR analysis but could still be evaluated here because no MR-estimates were used.]

@@

  plot_data <- corr_impact_by_traits %>% filter(trait_interest==trait) %>% filter(trait_interest!=trait_j)
  plot_data <- replace_Neale_ID(plot_data, traits_corr2_filled, "trait_j", "Phenotype")
  plot <-
    ggplot2::ggplot(
      data = plot_data,
      ggplot2::aes(x = trait_j_couple_corr,
                   y = corr_due_to_confounding, Phenotype = Phenotype)
    ) +
    theme(plot.title = element_text(hjust = 0.5)) +
    geom_point(alpha = 3 / 4) +

    ggplot2::geom_errorbar(
      ggplot2::aes(ymin = corr_due_to_confounding - corr_due_to_confounding_se, ymax = corr_due_to_confounding + corr_due_to_confounding_se),
      colour = "grey",
      width = 0
    ) +
    ggplot2::geom_errorbar(
      ggplot2::aes(xmin = trait_j_couple_corr - trait_j_couple_corr_se, xmax = trait_j_couple_corr + trait_j_couple_corr_se),
      colour = "grey",
      width = 0
    ) +

@@

```{r PC_confounder_plot, echo = FALSE, eval = FALSE, message=FALSE}

@@

plot_PCs <-
  ggplot2::ggplot(
    data = plot_data,
    ggplot2::aes(x = trait_couple_corr,
                 y = corr_due_to_confounding_all)
  ) +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_point(alpha = 3 / 4) +

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = corr_due_to_confounding_all - corr_due_to_confounding_all_se, ymax = corr_due_to_confounding_all + corr_due_to_confounding_all_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = trait_couple_corr - trait_couple_corr_se, xmax = trait_couple_corr + trait_couple_corr_se),
    colour = "grey",
    width = 0
  ) +

@@

  xlim(0, 1.0) +
  theme(plot.title = element_text(size=11, hjust = 0.5)) + theme(axis.title = element_text(size = 10))

i <- 5
plots[[i]] <- plot_PCs

@@

```{r coord_confounder_plot, echo = FALSE, eval = FALSE, message=FALSE, out.width = "200%", dpi=600}

plot_data <- corr_impact_by_coords %>% dplyr::select(Neale_pheno_ID, trait_couple_corr, corr_due_to_confounding_all, corr_due_to_confounding_all_se, trait_couple_corr_se, trait_couple_corr_se) %>% unique()

plot_coords <-
  ggplot2::ggplot(
    data = plot_data,
    ggplot2::aes(x = trait_couple_corr,
                 y = corr_due_to_confounding_all)
  ) +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_point(alpha = 3 / 4) +

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = corr_due_to_confounding_all - corr_due_to_confounding_all_se, ymax = corr_due_to_confounding_all + corr_due_to_confounding_all_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = trait_couple_corr - trait_couple_corr_se, xmax = trait_couple_corr + trait_couple_corr_se),
    colour = "grey",
    width = 0
  ) +

  theme_minimal() +
  ggplot2::labs(
    x = paste0("Couple trait correlation"),
    y = paste0("Couple correlation \ndue to confounding"),
    title = paste0("Place of birth \ncoordinates")
    #title = paste0("Impact of ", trait_description, "\n on couple correlation")
  ) +
  xlim(0, 1.0) +
  theme(plot.title = element_text(size=11, hjust = 0.5)) + theme(axis.title = element_text(size = 10))

i <- 6
plots[[i]] <- plot_coords

figures_grid <- plot_grid(plotlist = plots, nrow=3, ncol = 2, byrow = T, labels="AUTO", label_size = 12)
figures_grid

@@

  plot_data <- replace_Neale_ID(plot_data, traits_corr2_filled, "outcome_ID", "Phenotype")
  plot <-
    ggplot2::ggplot(
      data = plot_data,
      ggplot2::aes(x = outcome_ID_couple_r,
                   y = corr_due_to_confounding, Phenotype = Phenotype)
    ) +
    theme(plot.title = element_text(hjust = 0.5)) +
    geom_point(alpha = 3 / 4) +

    ggplot2::geom_errorbar(
      ggplot2::aes(ymin = corr_due_to_confounding - corr_due_to_confounding_se, ymax = corr_due_to_confounding + corr_due_to_confounding_se),
      colour = "grey",
      width = 0
    ) +
    ggplot2::geom_errorbar(
      ggplot2::aes(xmin = outcome_ID_couple_r - outcome_ID_couple_r_se, xmax = outcome_ID_couple_r + outcome_ID_couple_r_se),
      colour = "grey",
      width = 0
    ) +

@@

figures_grid <- plot_grid(plotlist = plots, nrow=2, ncol = 2, byrow = F, labels="AUTO")
figures_grid

@@

data <- proxyMR_comparison_summary_yiyp_adj_SNPmeta
data$rho_resid <- resid(lm(rho_beta ~ gam_beta, data = data))
data$gam_rho_resid <- data$rho_resid + data$gam_beta

@@

@@

figures_grid <- plot_grid(plotlist = list(proxyMR_prod_comparison_fig_yiyp_adj, boxplot), nrow=2, ncol = 1, byrow = T)
figures_grid

@@

file_name <- "docs/manuscript_tables/manuscript_tables.xlsx"

@@

write.xlsx_wrapper(corr_vs_MR_effects_sig_dat, file=file_name, sheetName="sig_corr_vs_MR", row.names=FALSE)
write.xlsx_wrapper(sig_confounders, file=file_name, sheetName="sig_confounders", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(AM_result_sig.DT, file=file_name, sheetName="BF_sig_same_trait_MR", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(nominally_sig_sex_differences, file=file_name, sheetName="nominally_sig_sex_diff", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(pheno_corr_pearson_sig.DT, file=file_name, sheetName="pheno_binned_corrs", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(corr_impact_by_traits_causal_summary, file=file_name, sheetName="corr_impact_ratios_summary", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(omega_regression_estimates, file=file_name, sheetName="omega_regression_estimates", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(paths_summary, file=file_name, sheetName="paths_summary", append=TRUE, row.names=FALSE)

>>>>

interesting_phenotypes <- c("Place of birth in UK - north co-ordinate", 
                            "Systolic blood pressure, automated reading", "Standing height", 
                            "Weight", "Forced vital capacity (FVC), Best measure",
                            "Basophill count", "Pulse rate, automated reading")

@@

corr_vs_MR_effects_plot <- ggplot2::ggplot(data = corr_vs_MR_effects_dat, ggplot2::aes(x = Correlation,
                                                       y = MR_est, 
                                                       label = Phenotype, 
                                                       color = factor(diff_p_sig)),) +

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = MR_est - 1.96*IVW_se, ymax = MR_est + 1.96*IVW_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = Correlation - 1.96*couple_r_se, xmax = Correlation + 1.96*couple_r_se),
    colour = "grey",
    width = 0
  ) +

  geom_point(alpha = 1.2) +
  scale_color_manual(values = custom_col[c(1,2)], labels=c("Non-significant","Bonferroni-significant difference")) +
  #geom_text(show.legend = FALSE) +
  geom_abline(slope=1, intercept=0) +

  theme_minimal() +
  theme(legend.text=element_text(size=11)) +
  #geom_text(aes(x=1,y=2,label=""),show.legend=F) +
  ggplot2::labs(x = paste0("Couple correlation"),
                y = paste("MR-estimate")) +
  theme(legend.position="bottom") + theme(legend.title=element_blank()) +
  geom_text_repel(data = subset(corr_vs_MR_effects_dat, label_phenos==TRUE),
                  nudge_y = -0.35 - subset(corr_vs_MR_effects_dat, label_phenos==TRUE)$MR_est, size = 3.25,
                  direction = "x", show.legend = FALSE, box.padding = 0.5 )

@@

number_of_potential_confounders <- dim(corr_potential_trait_confounders_pos)[1]/dim(corr_potential_trait_confounders_pos)[1]

@@

sig_confounders <- corr_potential_trait_confounders_pos %>% filter(sig_confounder) %>% group_by(outcome_ID) %>%
  arrange(-corr_due_to_confounding) %>%
  mutate(total_potential_confounders = n()) %>%
  dplyr::summarize(description = outcome_description[1],
                   total_potential_confounders = total_potential_confounders[1],
                   potential_confounders = paste0(exposure_description, collapse = "; "), 
                   max_C = max(corr_due_to_confounding)) %>%
  dplyr::rename(trait_ID = outcome_ID) %>%
  dplyr::rename(trait_description = description) %>% 
  dplyr::select(trait_description, trait_ID, everything())

sig_confounders_top5 <- corr_potential_trait_confounders_pos %>% filter(sig_confounder) %>% group_by(outcome_ID) %>%
  arrange(-corr_due_to_confounding) %>%
  mutate(total_potential_confounders = n()) %>%
  slice_head(n = 5) %>%
  #mutate(potential_confounders = paste0(exposure_description, collapse = "; ")) %>%
  dplyr::summarize(trait_description = outcome_description[1],
                   total_potential_confounders = total_potential_confounders[1],
                   top5_potential_confounders = paste0(exposure_description, collapse = "; "), 
                   max_C = max(corr_due_to_confounding)) %>%
  dplyr::rename(trait_ID = outcome_ID) %>%
  left_join(corr_vs_MR_effects_sig_dat.DT, by = c("trait_description", "trait_ID")) %>%
  dplyr::select(trait_description, trait_ID, couple_r, IVW_beta, IVW_pval,everything())

@@

```{r max_C_plot, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), message=FALSE, fig.height=10, dpi=600}

@@

  dplyr::rename(Z_beta = IVW_beta) %>%
  dplyr::rename(Z_se = IVW_se) %>%
  dplyr::rename(Z_pval = IVW_pval) %>%
  mutate(Z_sq_beta = Z_beta^2) %>%
  mutate(Z_sq_se = sqrt(4*Z_beta^2*Z_se^2+2*Z_se^4)) %>%
  dplyr::rename(Z_AM_beta = exposure_ID_AM_IVW_beta) %>%
  dplyr::rename(Z_AM_se = exposure_ID_AM_IVW_se) %>%
  mutate(Z_prod = Z_sq_beta*Z_AM_beta) %>%
  mutate(Z_prod_var = variance_of_product(Z_sq_beta, Z_sq_se, Z_AM_beta, Z_AM_se)) %>%
  mutate(Z_prod_se = sqrt(Z_prod_var)) %>%
  mutate(same_trait_corr_minus_MR_est_se = sqrt(variance_of_sum(outcome_ID_IVW_se, outcome_ID_couple_r_se))) %>%
  mutate(Phenotype = outcome_description) %>% 
  mutate(Phenotype = case_when(Phenotype == "Basal metabolic rate" ~ "BMR",
                               Phenotype == "Systolic blood pressure, automated reading" ~ "SBP",
                               Phenotype == "Pulse rate, automated reading" ~ "Pulse rate",
                               Phenotype == "Body fat percentage" ~ "BFP",
                               Phenotype == "Standing height" ~ "Height",
                               Phenotype == "Reticulocyte percentage" ~ "Reticulocyte %",

                               #Phenotype == "Weight" & outcome_ID == "21002_irnt" ~ "Weight",
                               Phenotype == "Forced vital capacity (FVC), Best measure" ~ "FVC",
                               Phenotype == "Red blood cell (erythrocyte) count" ~ "RBC count",
                               Phenotype == "Place of birth in UK - north co-ordinate" ~ "Place of birth, NC",
                               TRUE ~ Phenotype)) %>%
  mutate(label_phenos = case_when(outcome_description %in% interesting_phenotypes ~ TRUE, TRUE ~ FALSE))

max_C_plot <- ggplot2::ggplot(data = max_C_data, 
                              ggplot2::aes(x = corr_due_to_confounding, 
                                           y = same_trait_corr_minus_MR_est, 
                                           label = Phenotype)) +

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = same_trait_corr_minus_MR_est - 1.96*same_trait_corr_minus_MR_est_se, 
                 ymax = same_trait_corr_minus_MR_est + 1.96*same_trait_corr_minus_MR_est_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = corr_due_to_confounding - 1.96*Z_prod_se, 
                 xmax = corr_due_to_confounding + 1.96*Z_prod_se),
    colour = "grey",
    width = 0
  ) +

  geom_point(alpha = 1.2) +
  #scale_color_manual(values = custom_col[c(1,2)], labels=c("Non-significant","BF-signifncant difference")) +
  #geom_text(show.legend = FALSE) +
  geom_abline(slope=1, intercept=0) +

  theme_minimal() +
  ggplot2::labs(x = paste0("max C"),
                y = paste("Correlation - MR-estimate")) +
  theme(legend.title=element_blank()) +
  geom_text_repel(data = subset(max_C_data, label_phenos==TRUE),
                  nudge_y = -0.25 - subset(max_C_data, label_phenos==TRUE)$same_trait_corr_minus_MR_est, size = 3.25,
                  direction = "x", show.legend = FALSE, box.padding = 0.5)

@@

## combine `max_C_plot` with `corr_vs_MR_effects_plot`

corr_vs_MR_comb <- plot_grid(plotlist = list(corr_vs_MR_effects_plot, max_C_plot), nrow=2, ncol = 1, byrow = T, labels="AUTO")

corr_vs_MR_comb

@@

nominally_sig_sex_differences <- AM_result_sig_nom.DT %>% pivot_wider(names_from = exposure_sex, values_from = c(IVW_beta, IVW_se, IVW_pval))

@@

pheno_corr_pearson_sig <- binned_pheno_corr_summary %>% filter(bin_slope_pval_pearson < 0.05/num_tests_by_PCs) %>% arrange(desc(group))

@@

```{r, pheno_binned_figs, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), echo = FALSE, fig.height=7, dpi=600}

@@

## originally ran the confounder analysis using correlations only, but switched to use causal effects.

@@

@@

confounder_traits_sub <- confounder_traits[c(1,2,5,10,15)]

@@

corr_impact_by_PCs_summary <- corr_impact_by_PCs %>% 
  dplyr::select(Neale_pheno_ID, trait_couple_corr, trait_couple_corr_se, corr_due_to_confounding_all, corr_due_to_confounding_all_se) %>%
  unique() %>%
  mutate(confounder_trait = "PCs") %>%
  mutate(trait_ratio = corr_due_to_confounding_all/trait_couple_corr) %>%
  group_by(confounder_trait) %>%
  dplyr::summarise(mean_ratio = mean(trait_ratio), median_ratio = median(trait_ratio), sd_ratio = sd(trait_ratio), number_of_traits = n()) %>%
  mutate(confounder_trait_ID = NA)

corr_impact_by_coords_summary <- corr_impact_by_traits_causal %>% filter(exposure_ID=="129_irnt" | exposure_ID=="130_irnt") %>% 
  filter(!(outcome_ID=="129_irnt" | outcome_ID=="130_irnt"))  %>%
  group_by(outcome_ID) %>% mutate(corr_due_to_confounding_all = sum(corr_due_to_confounding)) %>%
  mutate(corr_due_to_confounding_all_se = sqrt(sum(corr_due_to_confounding_se^2))) %>%
  dplyr::select(outcome_ID, outcome_ID_couple_r, outcome_ID_couple_r_se, corr_due_to_confounding_all, corr_due_to_confounding_all_se) %>% unique() %>%
  mutate(confounder_trait = "Birth place coordinates") %>%
  mutate(trait_ratio = corr_due_to_confounding_all/outcome_ID_couple_r) %>%
  group_by(confounder_trait) %>%
  dplyr::summarise(mean_ratio = mean(trait_ratio), median_ratio = median(trait_ratio), sd_ratio = sd(trait_ratio), number_of_traits = n()) %>%
  mutate(confounder_trait_ID = NA)

corr_impact_summary <- rbind(corr_impact_by_traits_causal_summary, corr_impact_by_coords_summary)

corr_impact_summary %>%
  kbl() %>%
  kable_styling()

@@

@@

  plot_data <- corr_impact_by_traits %>% filter(trait_interest==trait) %>% filter(trait_interest!=trait_j)
  plot_data <- replace_Neale_ID(plot_data, traits_corr2_filled, "trait_j", "Phenotype")
  plot <-
    ggplot2::ggplot(
      data = plot_data,
      ggplot2::aes(x = trait_j_couple_corr,
                   y = corr_due_to_confounding, Phenotype = Phenotype)
    ) +

    ggplot2::geom_errorbar(
      ggplot2::aes(ymin = corr_due_to_confounding - 1.96*corr_due_to_confounding_se, ymax = corr_due_to_confounding + 1.96*corr_due_to_confounding_se),
      colour = "grey",
      width = 0
    ) +
    ggplot2::geom_errorbar(
      ggplot2::aes(xmin = trait_j_couple_corr - 1.96*trait_j_couple_corr_se, xmax = trait_j_couple_corr + 1.96*trait_j_couple_corr_se),
      colour = "grey",
      width = 0
    ) +

    theme(plot.title = element_text(hjust = 0.5)) +
    geom_point(alpha = 3 / 4) +

@@

```{r PC_confounder_plot, echo = FALSE, eval = TRUE, message=FALSE}

@@

plot_PCs <-
  ggplot2::ggplot(
    data = plot_data,
    ggplot2::aes(x = trait_couple_corr,
                 y = corr_due_to_confounding_all)
  ) +
  theme(plot.title = element_text(hjust = 0.5)) +

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = corr_due_to_confounding_all - 1.96*corr_due_to_confounding_all_se, ymax = corr_due_to_confounding_all + 1.96*corr_due_to_confounding_all_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = trait_couple_corr - 1.96*trait_couple_corr_se, xmax = trait_couple_corr + 1.96*trait_couple_corr_se),
    colour = "grey",
    width = 0
  ) +

  geom_point(alpha = 3 / 4) +

@@

  xlim(0, 1.0) +
  theme(plot.title = element_text(size=11, hjust = 0.5)) + theme(axis.title = element_text(size = 10))  +
  geom_abline(slope=1, intercept=0) +
  coord_cartesian(ylim = c(0, NA))

@@

```{r coord_confounder_plot, echo = FALSE, eval = TRUE, message=FALSE, out.width = "200%", dpi=600}

trait_description <- "Place of birth coordinates"

plot_data <- corr_impact_by_traits_causal %>% filter(exposure_ID=="129_irnt" | exposure_ID=="130_irnt") %>% 
  filter(!(outcome_ID=="129_irnt" | outcome_ID=="130_irnt"))  %>%
  group_by(outcome_ID) %>% mutate(corr_due_to_confounding_all = sum(corr_due_to_confounding)) %>%
  mutate(corr_due_to_confounding_all_se = sqrt(sum(corr_due_to_confounding_se^2))) %>%
  dplyr::select(outcome_ID, outcome_ID_couple_r, outcome_ID_couple_r_se, corr_due_to_confounding_all, corr_due_to_confounding_all_se) %>% unique()

plot_data <- replace_Neale_ID(plot_data, traits_corr2_filled, "outcome_ID", "Phenotype")
coord_plot <-
  ggplot2::ggplot(
    data = plot_data,
    ggplot2::aes(x = outcome_ID_couple_r,
                 y = corr_due_to_confounding_all, Phenotype = Phenotype)
  ) +
  theme(plot.title = element_text(hjust = 0.5)) +

  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = corr_due_to_confounding_all - 1.96*corr_due_to_confounding_all_se, ymax = corr_due_to_confounding_all + 1.96*corr_due_to_confounding_all_se),
    colour = "grey",
    width = 0
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(xmin = outcome_ID_couple_r - 1.96*outcome_ID_couple_r_se, xmax = outcome_ID_couple_r + 1.96*outcome_ID_couple_r_se),
    colour = "grey",
    width = 0
  ) +

  geom_point(alpha = 3 / 4) +

@@

  plot_data <- replace_Neale_ID(plot_data, traits_corr2_filled, "outcome_ID", "Phenotype")
  plot <-
    ggplot2::ggplot(
      data = plot_data,
      ggplot2::aes(x = outcome_ID_couple_r,
                   y = corr_due_to_confounding, Phenotype = Phenotype)
    ) +
    theme(plot.title = element_text(hjust = 0.5)) +

    ggplot2::geom_errorbar(
      ggplot2::aes(ymin = corr_due_to_confounding - 1.96*corr_due_to_confounding_se, ymax = corr_due_to_confounding + 1.96*corr_due_to_confounding_se),
      colour = "grey",
      width = 0
    ) +
    ggplot2::geom_errorbar(
      ggplot2::aes(xmin = outcome_ID_couple_r - 1.96*outcome_ID_couple_r_se, xmax = outcome_ID_couple_r + 1.96*outcome_ID_couple_r_se),
      colour = "grey",
      width = 0
    ) +

    geom_point(alpha = 3 / 4) +

@@

i <- 6
plots[[i]] <- coord_plot 
figures_grid <- plot_grid(plotlist = plots, nrow=3, ncol = 2, byrow = F, labels="AUTO")
figures_grid

@@

data <- proxyMR_comparison_summary_yiyp_adj_SNPmeta

data <- data %>%
  mutate(
    rho_larger = case_when(
      gam_vs_rho_BF_sig == TRUE & rho_beta > gam_beta ~ TRUE,
      gam_vs_rho_BF_sig == TRUE &
        rho_beta < gam_beta ~ FALSE,
      gam_vs_rho_BF_sig == FALSE ~ NA
    )
  ) %>%
  mutate(omega_larger = case_when((omega_beta - rho_beta - gam_beta) > max(rho_beta, gam_beta) ~ TRUE, 
                                  TRUE ~ FALSE))

data$rho_resid <- resid(lm(rho_beta ~ gam_beta, data = data))
data$gam_rho_resid <- data$rho_resid + data$gam_beta

@@

Of note, we found `r  table(data$gam_vs_rho_BF_sig)[[2]]` relationships which were significantly different between $\rho$ and  $\gamma$, whereby `r table(data$rho_larger)[[2]]` (`r (table(data$rho_larger)[[2]]/table(data$gam_vs_rho_BF_sig)[[2]])*100`%) showed larger effects through $\rho$ and the other `r table(data$rho_larger)[[1]]` (`r (table(data$rho_larger)[[1]]/table(data$gam_vs_rho_BF_sig)[[2]])*100`%) showed larger effects through $\gamma$.

@@

figures_grid <- plot_grid(plotlist = list(proxyMR_prod_comparison_fig_yiyp_adj, boxplot), nrow=2, ncol = 1, byrow = T, labels = c('', 'E'))
figures_grid

@@

main_tables_file <- "docs/manuscript_tables/manuscript_tables.xlsx"
supplementary_tables_file <- "docs/manuscript_tables/supplementary_tables.xlsx"

@@

## Main tables 
write.xlsx_wrapper(corr_impact_summary, file=main_tables_file, sheetName="Table 1 corr_impact_ratios_summary", row.names=FALSE)
write.xlsx_wrapper(omega_regression_estimates, file=main_tables_file, sheetName="Table 2 omega_regression_estimates", append=TRUE, row.names=FALSE)

## Supplementary tables
write.xlsx_wrapper(AM_result_sig.DT, file=supplementary_tables_file, sheetName="Table 1 BF_sig_same_trait_MR", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(nominally_sig_sex_differences, file=supplementary_tables_file, sheetName="Table 2 nominally_sig_sex_diff", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(pheno_corr_pearson_sig.DT, file=supplementary_tables_file, sheetName="Table 3 pheno_binned_corrs", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(corr_vs_MR_effects_sig_dat, file=supplementary_tables_file, sheetName="Table 4 sig_corr_vs_MR", row.names=FALSE)
write.xlsx_wrapper(sig_confounders, file=supplementary_tables_file, sheetName="Table 5 sig_confounders", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(paths_summary, file=supplementary_tables_file, sheetName="Table 6 paths_summary", append=TRUE, row.names=FALSE)
